I am greatly indebted to the mentors, instructors, departmental staff, friends, and family members who have supported me throughout my Ph.D. I am especially thankful for the mentorship of my advisor Charles Doering who  provided guidance throughout my studies. He has been a key element to my scientific and academic development. I would also like to gratefully acknowledge my committee members: Anthony Bloch, Jesse Capecelatro, Robert Deegan, and Mark Newman. Thank you for taking the time and effort to evaluate this work.

During my time at Michigan, I was fortunate to have many fruitful research discussions that impacted this work, especially those with Ian Tobasco, Karen Zaya, and Andre Souza. I also appreciate the helpful comments and feedback provided (some indirectly) on this work by Hongjie Dong, Luis Escauriaza, Guatum Iyer, Alexander Kiselev, Anna Mazzucato, and Christian Seis.

%I would like to thank Oliver Kripfgans who were involved in a M-Cubed collaborative research project on acoustic droplet vaporization (not included in this thesis) in my first half of my PhD. He and his lab members provided excellent guidance on conducting experiments. Thank you.
%
%I would like to give a special thanks to the Woods Hole Oceanographic Institution Geophysical Fluid Dynamics program which shaped my academic training during the summer of 2016. I was fortunate to work on active matter with Saverio Spagnolie and Michael Shelley who were great research mentors. Although this project does not appear in this thesis, this program definitely contributed to my academic development for which I am thankful.

Last but not least, I would like to sincerely thank Irene Park for always being supportive and caring throughout my graduate school years. She was always there for me and I am forever thankful. 